Astr 513: Homework 3

### 2016-04-04 HW3/HW3.tex
Updated question 2. Finished the ipython notebook.

>>>>

 \begin{figure}[ht]
  \centering
  \includegraphics[keepaspectratio]{figures/tully_fisher.eps}
  \caption{The magnitude and angular velocity form a power law.}
  \label{fig:tully_fisher}
 \end{figure}

We took our catalog and maximized the likelihood given in \autoref{eqn:ans1}.
Our raw data is shown in \autoref{fig:tully_fisher}, and the best
fit is shown in \autoref{fig:tully_fisher_fit}.

 \begin{figure}[ht]
  \centering
  \includegraphics[keepaspectratio]{figures/tully_fisher_fit.eps}
  \caption{The magnitude and angular velocity form a power law.
  The best fit Tully-Fisher relation is overplotted with the
  points from the galaxy catalog.}
  \label{fig:tully_fisher_fit}
 \end{figure}
